\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-03-16 k-planar.tex
Fixed broken reference

As an example of the use of layered partitions, to prove \cref{PlanarProduct}(a),
\citet{DJMMUW20} showed that every planar graph has an $H$-partition of layered width $1$ for some planar graph $H$ of treewidth at most $8$ (improved to $6$ in \cref{UWY}). The proof is constructive and gives a simple quadratic-time algorithm for finding the corresponding partition and layering. At the core of their work is the elegant proof by \citet{PS21} of the following result:

@@

	All that remains is to show that any triple of vertices of $H$ is contained in at most two bags of $\mathcal{T}$. By the inductive hypothesis, the only triples we need to be concerned about are the $3$-element subsets of  $\{x_0,x_1,\ldots,x_k\}$. The case $k=1$ is trivial since no triples can be formed by $\{x_0,x_1\}$.  When $k=2$, $B_{y_0}=\{x_0,x_1,x_2\}$.  In this case, the choice of $\tau$ ensures that there is at most one face $F_i$ of $M$ that has vertices of $S$, $P_1$, and $P_2$ on its boundary.  (Refer to \cref{boring_figure} to convince yourself of this.)  By the inductive hypothesis (applied to $H_i$) the bag $B_{z_i}$ is the only bag of $\mathcal{T}_i$ that contains $\{x_0,x_1,x_2\}$.  Therefore there are at most two bags, $B_y$ and $B_{z_i}$ of $\mathcal{T}$ that contain $\{x_0,x_1,x_2\}$.  This establishes (iii) for $k\in\{1,2\}$ so, from this point on we assume that $k=3$.

>>>>

As an example of the use of layered partitions, to prove \cref{PlanarProduct}(a),
\citet{DJMMUW20} showed that every planar graph has an $H$-partition of layered width $1$ for some planar graph $H$ of treewidth at most $8$ (improved to $6$ in \cite{UWY}). The proof is constructive and gives a simple quadratic-time algorithm for finding the corresponding partition and layering. At the core of their work is the elegant proof by \citet{PS21} of the following result:

@@

	All that remains is to show that any triple of vertices of $H$ is contained in at most two bags of $\mathcal{T}$. By the inductive hypothesis, the only triples we need to be concerned about are the $3$-element subsets of  $\{x_0,x_1,\ldots,x_k\}$. The case $k=1$ is trivial since no triples can be formed by $\{x_0,x_1\}$.  When $k=2$, $B_{y_0}=\{x_0,x_1,x_2\}$.  In this case, the fact that $\tau$ contains an edge $v_1v_2$ of $F$ with $v_1\in P_{x_1}$ and $v_2\in P_{x_2}$ ensures that there is at most one face $F_i$ of $M$ that has vertices of $S$, $P_1$, and $P_2$ on its boundary.  (Refer to the middle of \cref{boring_figure} to convince yourself of this.)  By the inductive hypothesis (applied to $H_i$) the bag $B_{z_i}$ is the only bag of $\mathcal{T}_i$ that contains $\{x_0,x_1,x_2\}$.  Therefore there are at most two bags, $B_y$ and $B_{z_i}$ of $\mathcal{T}$ that contain $\{x_0,x_1,x_2\}$.  This establishes (iii) for $k\in\{1,2\}$ so, from this point on we assume that $k=3$.
